Msc Thesis Figures

### 2020-07-18 Rmd/msc_thesis_figures.tex
pdf

\hypertarget{data-prep}{%
\subsubsection{Data prep}\label{data-prep}}

@@

We start by preparing the data from the outputs of scripts \texttt{7.1}
and \texttt{8.1}.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Results dir + mun shapefile}
\NormalTok{sce_dir_vec <-}\StringTok{ }\KeywordTok{list.files}\NormalTok{(}\StringTok{"libraries/stsim/monteregie-conncons-scripted.ssim.output"}\NormalTok{, }
                          \DataTypeTok{full.names =}\NormalTok{ T)}
\NormalTok{mun <-}\StringTok{ }\KeywordTok{st_read}\NormalTok{(}\StringTok{"data/mun/munic_SHP_clean.shp"}\NormalTok{, }\DataTypeTok{quiet =} \OtherTok{TRUE}\NormalTok{)}

\CommentTok{# results key}
\NormalTok{results_clean <-}\StringTok{ }\KeywordTok{read_rds}\NormalTok{(}\StringTok{"data/temp/stsim_run_results.RDS"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{select}\NormalTok{(scenarioId, name) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{name =}  \KeywordTok{gsub}\NormalTok{(.}\OperatorTok{$}\NormalTok{name, }\DataTypeTok{pattern =} \StringTok{" }\CharTok{\textbackslash{}\textbackslash{}}\StringTok{(.+}\CharTok{\textbackslash{}\textbackslash{}}\StringTok{)"}\NormalTok{, }\DataTypeTok{replacement =} \StringTok{""}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{sce =}  \KeywordTok{paste0}\NormalTok{(}\StringTok{"sce_"}\NormalTok{, .}\OperatorTok{$}\NormalTok{scenarioId)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{chapter =} \KeywordTok{c}\NormalTok{(}\StringTok{"none"}\NormalTok{, }\KeywordTok{rep}\NormalTok{(}\StringTok{"chap_1"}\NormalTok{, }\DecValTok{6}\NormalTok{), }\KeywordTok{rep}\NormalTok{(}\StringTok{"chap_2"}\NormalTok{, }\DecValTok{9}\NormalTok{))) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{splitted =} \KeywordTok{str_split}\NormalTok{(name, }\StringTok{" }\CharTok{\textbackslash{}\textbackslash{}}\StringTok{| "}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{climate =} \KeywordTok{unlist}\NormalTok{(}\KeywordTok{map}\NormalTok{(splitted, }\OperatorTok{~}\KeywordTok{unlist}\NormalTok{(.x[}\DecValTok{2}\NormalTok{])))) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{run =} \KeywordTok{unlist}\NormalTok{(}\KeywordTok{map}\NormalTok{(splitted, }\OperatorTok{~}\KeywordTok{unlist}\NormalTok{(.x[}\DecValTok{1}\NormalTok{])))) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{select}\NormalTok{(}\OperatorTok{-}\NormalTok{splitted) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{replace_na}\NormalTok{(}\KeywordTok{list}\NormalTok{(}\DataTypeTok{climate =} \StringTok{"none"}\NormalTok{))}

@@

@@

\CommentTok{# Joined dataset}
\NormalTok{joined <-}\StringTok{ }\KeywordTok{full_join}\NormalTok{(df_summarised, df_origin_summarised, }
                    \DataTypeTok{by=}\KeywordTok{c}\NormalTok{(}\StringTok{"sce"}\NormalTok{, }\StringTok{"source"}\NormalTok{, }\StringTok{"species"}\NormalTok{, }\StringTok{"timestep"}\NormalTok{, }\StringTok{"sum_cur"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(results_clean, }\DataTypeTok{by =} \StringTok{"sce"}\NormalTok{)  }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{replace_na}\NormalTok{(}\KeywordTok{list}\NormalTok{(}\DataTypeTok{climate =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{run =} \StringTok{"historic run"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\CommentTok{# Make factors}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{sce =} \KeywordTok{as.factor}\NormalTok{(sce), }\DataTypeTok{run =} \KeywordTok{as.factor}\NormalTok{(run), }\DataTypeTok{sum_cur =} \DecValTok{10}\OperatorTok{*}\NormalTok{(sum_cur),}
         \DataTypeTok{climate =} \KeywordTok{factor}\NormalTok{(climate, }\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"none"}\NormalTok{, }\StringTok{"historic"}\NormalTok{,}
                                              \StringTok{"baseline"}\NormalTok{, }\StringTok{"RCP 8.5"}\NormalTok{)),}
         \DataTypeTok{run =} \KeywordTok{factor}\NormalTok{(run, }\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"historic run"}\NormalTok{, }\StringTok{"BAU run"}\NormalTok{, }
                                      \StringTok{"BAU run + corrs protection"}\NormalTok{, }\StringTok{"BAU run + ref"}\NormalTok{, }
                                      \StringTok{"BAU run + corrs protection + ref"}\NormalTok{,}
                                      \StringTok{"BAU run + corrs protection + ref TARGETED"}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{theme_set}\NormalTok{(}\KeywordTok{theme_minimal}\NormalTok{())}
\KeywordTok{theme_update}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.85}\NormalTok{, }\FloatTok{0.22}\NormalTok{),}
             \CommentTok{#legend.justification = c(1, -0.2), # for inside plot}
             \CommentTok{#legend.position = "none",}
             \DataTypeTok{legend.box =} \StringTok{"vertical"}\NormalTok{,}
             \DataTypeTok{legend.background =} \KeywordTok{element_blank}\NormalTok{(),}
             \DataTypeTok{legend.box.background =} \KeywordTok{element_rect}\NormalTok{(}\DataTypeTok{colour =} \StringTok{"black"}\NormalTok{),}
             \DataTypeTok{panel.border =} \KeywordTok{element_rect}\NormalTok{(}\DataTypeTok{fill =} \OtherTok{NA}\NormalTok{),}
             \DataTypeTok{legend.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{15}\NormalTok{),}
             \DataTypeTok{legend.text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{12}\NormalTok{),}
             \DataTypeTok{plot.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{22}\NormalTok{),}
             \DataTypeTok{plot.subtitle =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{22}\NormalTok{),}
             \DataTypeTok{axis.text.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{angle=}\DecValTok{65}\NormalTok{, }\DataTypeTok{vjust=}\FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\DecValTok{15}\NormalTok{),}
             \DataTypeTok{axis.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =}\DecValTok{15}\NormalTok{),}
             \DataTypeTok{strip.text.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{15}\NormalTok{),}
             \DataTypeTok{strip.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{15}\NormalTok{),}
             \DataTypeTok{axis.title=}\KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{18}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\hypertarget{mean-current-flow-change-through-time---historic}{%
\paragraph{Mean current flow change through time -
historic}\label{mean-current-flow-change-through-time---historic}}

@@

\begin{figure}
\includegraphics[width=1.5\linewidth]{msc_thesis_figures_files/figure-latex/fig_1_historic-1} \caption{Connectivity change for species through time, 1990-2010}\label{fig:fig_1_historic}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggsave}\NormalTok{(fig_}\DecValTok{1}\NormalTok{_historic,}
       \DataTypeTok{filename =} \StringTok{"outputs/figures/connectivity_decrease_x5species_historic.png"}\NormalTok{,}
       \DataTypeTok{width =} \DecValTok{17}\NormalTok{, }\DataTypeTok{height =} \DecValTok{12}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{mean-current-flow-change-through-time---chap-1}{%
\subparagraph{Mean current flow change through time - chap
1}\label{mean-current-flow-change-through-time---chap-1}}

>>>>

{
\setcounter{tocdepth}{5}
\tableofcontents
}
\hypertarget{data-prep}{%
\subsubsection{Data prep}\label{data-prep}}

@@

We start by preparing the data from the outputs of scripts \texttt{7.1}
and \texttt{8.1}. The results table shown as output is the key to read
the figures.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Results dir + mun shapefile}
\NormalTok{mun <-}\StringTok{ }\KeywordTok{st_read}\NormalTok{(}\StringTok{"data/mun/munic_SHP_clean.shp"}\NormalTok{, }\DataTypeTok{quiet =} \OtherTok{TRUE}\NormalTok{)}

\CommentTok{# results key}
\NormalTok{sce_code_vec <-}\StringTok{ }
\StringTok{  }\KeywordTok{as.vector}\NormalTok{(}\KeywordTok{t}\NormalTok{(}\KeywordTok{outer}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"BAU-"}\NormalTok{, }\StringTok{"R-"}\NormalTok{, }\StringTok{"CorPr-"}\NormalTok{, }\StringTok{"R-CorPr-"}\NormalTok{, }\StringTok{"R(T)-CorPr-"}\NormalTok{), }
                    \KeywordTok{c}\NormalTok{(}\StringTok{"Hist"}\NormalTok{, }\StringTok{"Base"}\NormalTok{, }\StringTok{"RCP8"}\NormalTok{), paste0)))}
\NormalTok{sce_code_vec_run <-}\StringTok{ }
\StringTok{  }\KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"BAU"}\NormalTok{, }\StringTok{"R"}\NormalTok{, }\StringTok{"CorPr"}\NormalTok{, }\StringTok{"R-CorPr"}\NormalTok{, }\StringTok{"R(T)-CorPr"}\NormalTok{), }\DataTypeTok{each=}\DecValTok{3}\NormalTok{)}

\NormalTok{results_clean <-}\StringTok{ }\KeywordTok{read_rds}\NormalTok{(}\StringTok{"data/temp/stsim_run_results.RDS"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{select}\NormalTok{(scenarioId, name) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{name =}  \KeywordTok{gsub}\NormalTok{(.}\OperatorTok{$}\NormalTok{name, }\DataTypeTok{pattern =} \StringTok{" }\CharTok{\textbackslash{}\textbackslash{}}\StringTok{(.+}\CharTok{\textbackslash{}\textbackslash{}}\StringTok{)"}\NormalTok{, }\DataTypeTok{replacement =} \StringTok{""}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{sce =}  \KeywordTok{paste0}\NormalTok{(}\StringTok{"sce_"}\NormalTok{, .}\OperatorTok{$}\NormalTok{scenarioId)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{chapter =} \KeywordTok{c}\NormalTok{(}\StringTok{"none"}\NormalTok{, }\KeywordTok{rep}\NormalTok{(}\StringTok{"both"}\NormalTok{, }\DecValTok{3}\NormalTok{), }\KeywordTok{rep}\NormalTok{(}\StringTok{"chap_1"}\NormalTok{, }\DecValTok{3}\NormalTok{), }\KeywordTok{rep}\NormalTok{(}\StringTok{"chap_2"}\NormalTok{, }\DecValTok{9}\NormalTok{))) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{splitted =} \KeywordTok{str_split}\NormalTok{(name, }\StringTok{" }\CharTok{\textbackslash{}\textbackslash{}}\StringTok{| "}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{climate =} \KeywordTok{unlist}\NormalTok{(}\KeywordTok{map}\NormalTok{(splitted, }\OperatorTok{~}\KeywordTok{unlist}\NormalTok{(.x[}\DecValTok{2}\NormalTok{])))) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{run =} \KeywordTok{unlist}\NormalTok{(}\KeywordTok{map}\NormalTok{(splitted, }\OperatorTok{~}\KeywordTok{unlist}\NormalTok{(.x[}\DecValTok{1}\NormalTok{])))) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{select}\NormalTok{(}\OperatorTok{-}\NormalTok{splitted) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{replace_na}\NormalTok{(}\KeywordTok{list}\NormalTok{(}\DataTypeTok{climate =} \StringTok{"none"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{code =} \KeywordTok{c}\NormalTok{(}\StringTok{"Control"}\NormalTok{, sce_code_vec)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{code_run =} \KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, sce_code_vec_run))}

@@

\CommentTok{# Stratum key}
\NormalTok{stratum_key <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"config/stsim/SecondaryStratum.csv"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{ID =} \KeywordTok{as.factor}\NormalTok{(ID)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{zone=}\NormalTok{ID, }\DataTypeTok{MUS_NM_MUN=}\NormalTok{Name) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{left_join}\NormalTok{(df_final, }\DataTypeTok{by=}\StringTok{"zone"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(MUS_NM_MUN}\OperatorTok{!=}\StringTok{"Not Monteregie"}\NormalTok{)}

@@

\CommentTok{# Joined dataset}
\NormalTok{joined <-}\StringTok{ }\KeywordTok{full_join}\NormalTok{(df_summarised, df_origin_summarised, }
                    \DataTypeTok{by=}\KeywordTok{c}\NormalTok{(}\StringTok{"sce"}\NormalTok{, }\StringTok{"source"}\NormalTok{, }\StringTok{"species"}\NormalTok{, }\StringTok{"timestep"}\NormalTok{, }\StringTok{"sum_cur"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(results_clean, }\DataTypeTok{by =} \StringTok{"sce"}\NormalTok{)  }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{replace_na}\NormalTok{(}\KeywordTok{list}\NormalTok{(}\DataTypeTok{climate =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{run =} \StringTok{"historic run"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\CommentTok{# Make factors}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{sce =} \KeywordTok{as.factor}\NormalTok{(sce), }\DataTypeTok{run =} \KeywordTok{as.factor}\NormalTok{(run), }\DataTypeTok{sum_cur =} \DecValTok{10}\OperatorTok{*}\NormalTok{(sum_cur),}
         \DataTypeTok{climate =} \KeywordTok{factor}\NormalTok{(climate, }\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"none"}\NormalTok{, }\StringTok{"historic"}\NormalTok{,}
                                              \StringTok{"baseline"}\NormalTok{, }\StringTok{"RCP 8.5"}\NormalTok{)),}
         \DataTypeTok{run =} \KeywordTok{factor}\NormalTok{(run, }\DataTypeTok{levels =} \KeywordTok{c}\NormalTok{(}\StringTok{"historic run"}\NormalTok{, }\StringTok{"BAU run"}\NormalTok{, }
                                      \StringTok{"BAU run + corrs protection"}\NormalTok{, }\StringTok{"BAU run + ref"}\NormalTok{, }
                                      \StringTok{"BAU run + corrs protection + ref"}\NormalTok{,}
                                      \StringTok{"BAU run + corrs protection + ref TARGETED"}\NormalTok{)))}

\CommentTok{# Roc curves data}
\NormalTok{urb <-}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(}\StringTok{"data/temp/fit_rs_outcome_rf_urb_2.RDS"}\NormalTok{)}
\NormalTok{agex <-}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(}\StringTok{"data/temp/fit_rs_outcome_rf_agex_2.RDS"}\NormalTok{)}

\CommentTok{# Histogram data }
\NormalTok{histograms <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"outputs/final/final_values_output.csv"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(results_clean, }\DataTypeTok{by=}\StringTok{"sce"}\NormalTok{)}

\CommentTok{# SURF Data}
\NormalTok{surf <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"surf/surf_output.csv"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{timestep =}\NormalTok{ timestep}\OperatorTok{*}\DecValTok{10}\OperatorTok{+}\DecValTok{1990}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(results_clean, }\DataTypeTok{by=}\KeywordTok{c}\NormalTok{(}\StringTok{"scenario"}\NormalTok{=}\StringTok{"scenarioId"}\NormalTok{))}

\NormalTok{results_clean}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##    scenarioId                                                 name    sce
## 1          37                                         historic run sce_37
## 2          38                                   BAU run | historic sce_38
## 3          39                                   BAU run | baseline sce_39
## 4          40                                    BAU run | RCP 8.5 sce_40
## 5          41                             BAU run + ref | historic sce_41
## 6          42                             BAU run + ref | baseline sce_42
## 7          43                              BAU run + ref | RCP 8.5 sce_43
## 8          44                BAU run + corrs protection | historic sce_44
## 9          45                BAU run + corrs protection | baseline sce_45
## 10         46                 BAU run + corrs protection | RCP 8.5 sce_46
## 11         47          BAU run + corrs protection + ref | historic sce_47
## 12         48          BAU run + corrs protection + ref | baseline sce_48
## 13         49           BAU run + corrs protection + ref | RCP 8.5 sce_49
## 14         50 BAU run + corrs protection + ref TARGETED | historic sce_50
## 15         51 BAU run + corrs protection + ref TARGETED | baseline sce_51
## 16         52  BAU run + corrs protection + ref TARGETED | RCP 8.5 sce_52
##    chapter  climate                                       run            code
## 1     none     none                              historic run         Control
## 2     both historic                                   BAU run        BAU-Hist
## 3     both baseline                                   BAU run        BAU-Base
## 4     both  RCP 8.5                                   BAU run        BAU-RCP8
## 5   chap_1 historic                             BAU run + ref          R-Hist
## 6   chap_1 baseline                             BAU run + ref          R-Base
## 7   chap_1  RCP 8.5                             BAU run + ref          R-RCP8
## 8   chap_2 historic                BAU run + corrs protection      CorPr-Hist
## 9   chap_2 baseline                BAU run + corrs protection      CorPr-Base
## 10  chap_2  RCP 8.5                BAU run + corrs protection      CorPr-RCP8
## 11  chap_2 historic          BAU run + corrs protection + ref    R-CorPr-Hist
## 12  chap_2 baseline          BAU run + corrs protection + ref    R-CorPr-Base
## 13  chap_2  RCP 8.5          BAU run + corrs protection + ref    R-CorPr-RCP8
## 14  chap_2 historic BAU run + corrs protection + ref TARGETED R(T)-CorPr-Hist
## 15  chap_2 baseline BAU run + corrs protection + ref TARGETED R(T)-CorPr-Base
## 16  chap_2  RCP 8.5 BAU run + corrs protection + ref TARGETED R(T)-CorPr-RCP8
##      code_run
## 1     control
## 2         BAU
## 3         BAU
## 4         BAU
## 5           R
## 6           R
## 7           R
## 8       CorPr
## 9       CorPr
## 10      CorPr
## 11    R-CorPr
## 12    R-CorPr
## 13    R-CorPr
## 14 R(T)-CorPr
## 15 R(T)-CorPr
## 16 R(T)-CorPr
\end{verbatim}

Preparing for spatial plotting (time consuming).

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Pivoted dataset for mapping}
\CommentTok{# df_final_fordiff_pivoted <- df_final %>% }
\CommentTok{#   left_join(results_clean, by = "sce")  %>% }
\CommentTok{#   group_by(zone, sce, species, timestep, source, chapter) %>% }
\CommentTok{#   summarise(current = mean(current)) %>% ungroup %>% }
\CommentTok{#   filter(timestep %in% c(2010, last(unique(stratum_key$timestep)))) %>% }
\CommentTok{#   pivot_wider(names_from=timestep, values_from=current) %>% drop_na() %>% }
\CommentTok{#   rename(before=last_col(offset = 1), after=last_col()) %>% }
\CommentTok{#   left_join(stratum_key, by=c("zone", "sce", "species", "source")) %>% }
\CommentTok{#   filter(MUS_NM_MUN!="Not Monteregie") %>% }
\CommentTok{#   mutate(change=((after-before)/before)*100) %>% }
\CommentTok{#   left_join(mun, by="MUS_NM_MUN") %>% }
\CommentTok{#   st_as_sf()}
\CommentTok{# }
\CommentTok{# df_final_fordiff_pivoted <- }
\CommentTok{#   st_transform(df_final_fordiff_pivoted, crs=4326)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{theme_set}\NormalTok{(}\KeywordTok{theme_minimal}\NormalTok{())}
\KeywordTok{theme_update}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.85}\NormalTok{, }\FloatTok{0.20}\NormalTok{),}
             \CommentTok{#legend.justification = c(1, -0.2), # for inside plot}
             \CommentTok{#legend.position = "none",}
             \DataTypeTok{legend.box =} \StringTok{"vertical"}\NormalTok{,}
             \DataTypeTok{legend.background =} \KeywordTok{element_blank}\NormalTok{(),}
             \DataTypeTok{legend.box.background =} \KeywordTok{element_rect}\NormalTok{(}\DataTypeTok{colour =} \StringTok{"black"}\NormalTok{),}
             \DataTypeTok{panel.border =} \KeywordTok{element_rect}\NormalTok{(}\DataTypeTok{fill =} \OtherTok{NA}\NormalTok{),}
             \DataTypeTok{legend.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{10}\NormalTok{),}
             \DataTypeTok{legend.text =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{8}\NormalTok{),}
             \DataTypeTok{plot.title =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{20}\NormalTok{),}
             \DataTypeTok{plot.subtitle =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{20}\NormalTok{),}
             \DataTypeTok{axis.text.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{angle=}\DecValTok{65}\NormalTok{, }\DataTypeTok{vjust=}\FloatTok{0.6}\NormalTok{, }\DataTypeTok{size =}\DecValTok{13}\NormalTok{),}
             \DataTypeTok{axis.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =}\DecValTok{10}\NormalTok{),}
             \DataTypeTok{strip.text.x =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{10}\NormalTok{),}
             \DataTypeTok{strip.text.y =} \KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size =} \DecValTok{10}\NormalTok{),}
             \DataTypeTok{axis.title=}\KeywordTok{element_text}\NormalTok{(}\DataTypeTok{size=}\DecValTok{15}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\hypertarget{mean-current-flow-change}{%
\subsubsection{Mean current flow
change}\label{mean-current-flow-change}}

\hypertarget{historic}{%
\paragraph{Historic}\label{historic}}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{msc_thesis_figures_files/figure-latex/fig_1_historic-1} \caption{Connectivity change for species through time, 1990-2010}\label{fig:fig_1_historic}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggsave}\NormalTok{(fig_}\DecValTok{1}\NormalTok{_historic,}
       \DataTypeTok{filename =} \StringTok{"outputs/figures/connectivity_decrease_x5species_historic.png"}\NormalTok{,}
       \DataTypeTok{width =} \DecValTok{15}\NormalTok{, }\DataTypeTok{height =} \DecValTok{10}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{chap-1}{%
\paragraph{Chap 1}\label{chap-1}}

\hypertarget{line-graph}{%
\subparagraph{Line graph}\label{line-graph}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{fig_}\DecValTok{1}\NormalTok{_static_chap_}\DecValTok{1}\NormalTok{ <-}\StringTok{ }\NormalTok{joined }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(climate }\OperatorTok{!=}\StringTok{ "none"}\NormalTok{, chapter }\OperatorTok{%in%}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"none"}\NormalTok{, }\StringTok{"both"}\NormalTok{, }\StringTok{"chap_1"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{group_by}\NormalTok{(scenarioId, species, iteration) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{group_modify}\NormalTok{(}\OperatorTok{~}\KeywordTok{mutate}\NormalTok{(.x , }\DataTypeTok{baseline =} \KeywordTok{subset}\NormalTok{(.x, timestep }\OperatorTok{==}\StringTok{ }\DecValTok{2010}\NormalTok{)}\OperatorTok{$}\NormalTok{sum_cur, }
                       \DataTypeTok{the_diff =}\NormalTok{ ((sum_cur}\OperatorTok{-}\NormalTok{baseline)}\OperatorTok{/}\NormalTok{baseline)}\OperatorTok{*}\DecValTok{100}\NormalTok{ )) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{timestep, }\DataTypeTok{y=}\NormalTok{the_diff, }\DataTypeTok{col=}\NormalTok{climate)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_color_manual}\NormalTok{(}\DataTypeTok{values=}\KeywordTok{c}\NormalTok{(}\StringTok{'#ffe300'}\NormalTok{, }\StringTok{'#ff7a14'}\NormalTok{, }\StringTok{"#b31400"}\NormalTok{), }
                     \DataTypeTok{labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"Historic"}\NormalTok{, }\StringTok{"Baseline"}\NormalTok{, }\StringTok{"RCP 8.5"}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_smooth}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{group =}\NormalTok{ sce, }\DataTypeTok{linetype=}\NormalTok{code_run), }\DataTypeTok{alpha=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{method=}\StringTok{"loess"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_linetype_manual}\NormalTok{(}\DataTypeTok{values=}\KeywordTok{c}\NormalTok{(}\StringTok{"solid"}\NormalTok{, }\StringTok{"twodash"}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{facet_wrap}\NormalTok{(}\OperatorTok{~}\NormalTok{species, }\DataTypeTok{scales =} \StringTok{"fixed"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_hline}\NormalTok{(}\DataTypeTok{yintercept =} \DecValTok{0}\NormalTok{, }\DataTypeTok{linetype =} \StringTok{"dashed"}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{0.5}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_vline}\NormalTok{(}\DataTypeTok{xintercept =} \DecValTok{2020}\NormalTok{, }\DataTypeTok{linetype =} \StringTok{"dashed"}\NormalTok{, }\DataTypeTok{color =} \StringTok{"darkGreen"}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{0.5}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{y =} \StringTok{"Current flow (% Change)"}\NormalTok{,}
       \DataTypeTok{x =} \StringTok{"Year"}\NormalTok{,}
       \DataTypeTok{col =} \StringTok{"Climate"}\NormalTok{,}
       \DataTypeTok{linetype =} \StringTok{"Run"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{guides}\NormalTok{(}\DataTypeTok{col =} \KeywordTok{guide_legend}\NormalTok{(}\DataTypeTok{ncol =} \DecValTok{2}\NormalTok{, }\DataTypeTok{nrow=}\DecValTok{2}\NormalTok{), }
         \DataTypeTok{linetype =} \KeywordTok{guide_legend}\NormalTok{(}\DataTypeTok{nrow=}\DecValTok{1}\NormalTok{, }\DataTypeTok{override.aes =} \KeywordTok{list}\NormalTok{(}\DataTypeTok{colour =} \StringTok{'black'}\NormalTok{))) }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.85}\NormalTok{, }\FloatTok{0.15}\NormalTok{))}\OperatorTok{+}
\StringTok{  }\OtherTok{NULL}
\NormalTok{fig_}\DecValTok{1}\NormalTok{_static_chap_}\DecValTok{1}
\end{Highlighting}
\end{Shaded}

\begin{figure}
\includegraphics[width=1\linewidth]{msc_thesis_figures_files/figure-latex/figure_1_model_1-1} \caption{Connectivity change for species through time, 2010-2100}\label{fig:figure_1_model_1}
\end{figure}
